---
title: "Museums per capita"
output:
  html_document:
    df_print: paged
---

```{r echo=FALSE}

knitr::opts_chunk$set(message = FALSE, warning = FALSE)

```

<blockquote class="twitter-tweet" data-lang="en"><p lang="en" dir="ltr">Here&#39;s a nice random fact for you: NZ has a high number of museums per capita. 2013 was 1:9,500. <br><br>Same year, UK was 1:17,000, the US 1:24,000. 2008 Australia was 1:18,000. <br><br>~55,000 museums globally, approx one for every 146,000 people. NZ is well ahead of the bell curve!</p>&mdash; Scott Pilkington (@spil030) <a href="https://twitter.com/spil030/status/1109732472240009217?ref_src=twsrc%5Etfw">March 24, 2019</a></blockquote>
<script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>


```{r libraries}

library(tidyverse)
library(rvest)
library(gapminder)

```

# Getting some comparison countries

I decided to grab some countries with populations within a million of New Zealands. The easiest dataset I new with loads of population data is in the lovely `gapminder` package. Unfortunately the most recent population counts are for 2007, but this attempt is so back-of-the-envelope anyway, and more just a chance to play, so I'm going to just go with that. Also provides GDP per capita which I think is interesting for arts and culture funding.

```{r}
my_pop = gapminder %>% 
  filter(year == max(year)) %>% 
  mutate(NZpop = ifelse(country == "New Zealand", pop, NA)) %>% 
  mutate(NZpop = as.numeric(NZpop)) %>% 
  arrange(NZpop) %>% 
  fill(NZpop) %>% 
  mutate(`Difference from NZ` = pop-NZpop) %>% 
  filter(abs(`Difference from NZ`) < 1000000)

```

# Examples of getting number of museums from Wikipedia lists

Below are a couple very messy examples of scraping the individual pages on Wikipedia:

```{r messy}

NZ = read_html("https://en.wikipedia.org/wiki/List_of_museums_in_New_Zealand") %>% 
  html_nodes("ul") %>% 
  html_text() %>% 
  as.data.frame() %>% 
  .[3:22,] %>% 
  as.data.frame() %>% 
  rename(name = 1) %>% 
  separate_rows(name, sep = "\\\n") 

nrow(NZ)

ireland = read_html("https://en.wikipedia.org/wiki/List_of_museums_in_the_Republic_of_Ireland") %>% 
  html_nodes("table") %>% 
  .[[2]] %>% 
  html_table(fill = TRUE)

nrow(ireland)

norway = read_html("https://en.wikipedia.org/wiki/List_of_museums_in_Norway") %>% 
  html_nodes("ul") %>% 
  html_text() %>% 
  as.data.frame() %>% 
  .[3:22,] %>% 
  data_frame() %>% 
  rename(name = 1) %>% 
  separate_rows(name, sep = "\\\n")
nrow(norway)

oman = read_html("https://en.wikipedia.org/wiki/List_of_museums_in_Oman") %>% 
  html_nodes("ul") %>% 
  html_text() %>% 
  as.data.frame() %>% 
  .[1,] %>% 
  data_frame() %>% 
  rename(name = 1) %>% 
  separate_rows(name, sep = "\\\n")
nrow(oman)

panama = read_html("https://en.wikipedia.org/wiki/List_of_museums_in_Panama") %>% 
  html_nodes("table") %>% 
  .[[1]] %>% 
  html_table(fill = TRUE)
nrow(panama)

puertorico = read_html("https://en.wikipedia.org/wiki/List_of_museums_in_Puerto_Rico") %>% 
  html_nodes("table") %>% 
  .[[2]] %>% 
  html_table(fill = TRUE)
nrow(puertorico)

singapore = read_html("https://en.wikipedia.org/wiki/List_of_museums_in_Singapore") %>% 
  html_nodes("ul") %>% 
  html_text() %>% 
  as.data.frame() %>% 
  .[2:4,] %>% 
  data_frame() %>% 
  rename(name = 1) %>% 
  separate_rows(name, sep = "\\\n")
nrow(singapore)

uruguay = read_html("https://en.wikipedia.org/wiki/List_of_museums_in_Uruguay") %>% 
  html_nodes("ul") %>% 
  html_text() %>% 
  as.data.frame() %>% 
  .[1,] %>% 
  data_frame() %>% 
  rename(name = 1) %>% 
  separate_rows(name, sep = "\\\n")
nrow(uruguay)

```

The ideal would be to use the [main page](https://en.wikipedia.org/wiki/List_of_museums_by_country) to get all the hyperlinks with something like this:

```{r, eval = FALSE}

get_links = read_html("https://en.wikipedia.org/wiki/List_of_museums_by_country") %>% 
  html_nodes("a") %>% 
  html_attr("href") %>% 
  data.frame() %>% 
  rename(links = 1) %>% 
  filter(grepl("wiki/List_of_museums_in", links)) %>% 
  mutate(links = paste0("https://en.wikipedia.org/", links))


```

...and then scrape each of these, but aside from there being several ways these pages are formatted, you also have some lists just under the country title, not linking to a new page, and then you have some missing (I think Republic of Congo's list of museums is missing from this main page). Ugh.

# Making a graph
So here is a quick look at the number of museums per 100,000 people. There are quite a few limitations on the data of course, but interesting none the less, I hope.

```{r fig.width=9, fig.height=5}
# numbers mostly by hand from wikipedia

museums = read_csv("museums.csv")

tidy_museums = museums %>% 
  mutate(`Museums per 100,000` = `N museums from Wikipedia`/pop*100000) %>% 
  filter(!is.na(country))

tidy_museums %>% 
  mutate(country = fct_reorder(country, `Museums per 100,000`)) %>% 
  ggplot(aes(x = `Museums per 100,000`, y = country, size = gdpPerCap, color = continent)) +
  geom_point() +
  scale_size_continuous(name = "GDP per capita (2007)") +
  scale_color_discrete(name = "Continent") +
  ylab(label = "Country") +
  xlab(label = "Museums per 100,000 people") +
  theme_minimal() +
  ggtitle("Museums per 100,000 people") +
  labs(caption = "More info: Countries were included based on being +/- 1 million the population of\nNew Zealand in 2007, based on Gapminder data. Museum counts were\ndone by hand based on lists on Wikipedia and may be wildly wrong.")

```

Code and data available at [https://github.com/elb0/museums-per-capita]().